Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-19 Paper.tex
Byzantium revision

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity (formerly Ethcore)\\
    i@gavwood.com\footnote{Please talk to maintainers on Github such as @pirapira and @nicksavers, only contact Gavin with their permission.}
}
\begin{document}

>>>>

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Ethcore\\
    gavin@ethcore.io
}
\begin{document}
